Self Regulation Ontology Retest Analyses

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

numeric_cols = c()

for(i in 1:length(names(test_data))){
  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
    numeric_cols <- c(numeric_cols, names(test_data)[i])
  }
}
#Create df of point estimate reliabilities
rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)),
                     pearson = rep(NA, length(numeric_cols)),
                     partial_eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)),
                     var_subs = rep(NA, length(numeric_cols)),
                     var_ind = rep(NA, length(numeric_cols)),
                     var_resid = rep(NA, length(numeric_cols)))

row.names(rel_df) <- numeric_cols

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i])
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
}

rel_df$dv = row.names(rel_df)
row.names(rel_df) = seq(1:nrow(rel_df))
rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
# row.names(rel_df) = NULL

@@

```{r}
table(rel_df$task)
```

>>>>

rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
```

@@
